---
title: "NHSRpostcodetools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NHSRpostcodetools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = TRUE,
  eval = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Checking for valid postcodes

```{r setup}
library(NHSRpostcodetools)
```

Both vectors and tibbles can be passed through the functions. 
Starting with a vector of postcodes with the first being terminated, the second  
is valid and the third is invalid.

### A vector of postcodes

```{r}
# a vector
postcodes <- c("HD1 2UT", "HD1 2UU", "HD1 2UV")
```

Join this vector to the postcode data

```{r}
postcode_data_join(postcodes, fix_invalid = TRUE)

```

### A tibble of postcodes

```{r}
test_df1 <- dplyr::tibble(
  place = paste0("place_", 1:3),
  postcode = postcodes
)
```

For a tibble or data frame the code to extract to pass through the functions in
this package the postcode column needs to be recoded to `postcodes` in order
to be recognised.

```{r}
postcode_data_join(test_df1, fix_invalid = TRUE)

```

