---
title: The postcodes.io API schema
vignette: >
  %\VignetteIndexEntry{The postcodes.io API schema}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
df-print: tibble
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

```{r}
#| label: setup
library(NHSRpostcodetools)
```

The package contains two items of data.
One that is available to the user is a copy of the postcodes.io API postcode
data schema, as published at [https://postcodes.io/docs/postcode/schema][sch]

[sch]: https://postcodes.io/docs/postcode/schema

This can be accessed with

```{r}
#| label: schema_table
schema_table
```


A vector of all the field names in the schema is also available, but only as
internal data, which means you will need to use `:::` to access it:

```{r}
#| label: schema_fields
NHSRpostcodetools:::schema_fields
```

This vector may be useful if you want to construct a custom vector of fields
to pass to `filter_fields()`.

`schema_fields` is actually identical to the `field` column in `schema_table`:

```{r}
#| label: ident
identical(NHSRpostcodetools:::schema_fields, schema_table[["field"]])
```
